Multi-Domain Adaptation in Neural Machine Translation with Dynamic Sampling Strategies

### 2021-05-12 2021/emnlp/auto_cl_mdmt.tex
fix some lambda, resolve fixmes

\section{Introduction}\label{sec:intro}
A typical setting in machine translation (MT) is to collect the largest possible collection of parallel data for the chosen language pair, with the intent to achieve optimal performance for a task of interest. In such situations, the training data distribution is opportunistic, while the test data distribution is chosen and fixed; a key component in training is then to mitigate the detrimental effects of a possible mismatch between these distributions. Single-source and multi-source domain adaptation (DA) is a well-studied instance of this setting (see \citet{Chu2017comparison} for a review), and so is multi-domain (MD) learning \citep{Chu18multilingual,Zeng18multidomain,Jiang19multidomain,Pham21revisiting}. A related situation is multilingual machine translation \citep{Firat16multiway,Ha16towards,Johnson17google,Arivazhagan19massively}\fyTodo{Add more recent work} \revision{cite also \citep{shen21source}}, where the heterogeneity of training data not only corresponds to variations in topic, genre or register, but also in language.

@@

To compute the reward $R(d)$ of using data from domain $d$ to train the model, we simulate $k$ training steps from current checkpoint by training the model with $k$ batches sampled from $D^l(d)$ and compute the gain of the weighted dev-loss. This computation is inspired by the target prediction gain in \citep{Graves17automated}. However, \cite{Graves17automated} used accumulated gains from the past as reward, while we predict the usefulness of each domain for improving the future performance of the system given its current state. This is achieved by simulating a round of training with only the data from one domain. Furthermore, the choice of the parameterization of the sampling distribution in our method differs from that of \citet{Graves17automated}, although this choice is empirical.

The work of \cite{Wang20balancing} is also related: it is based on the Bi-level Optimization framework, which aims to find an optimal static distribution $\lambda^{l}$ that will result in the best NMT model with respect to a given target dev set at the end of training. These authors also derive a similar form of update for $\psi$. However, their reward is the cosine similarity between the gradient computed with the training data from one domain and the gradient computed with the dev set. We compare this approach with ours in the experiment section.

\subsection{MDAC for (multi) domain adaptation}
The setting developed in previous sections is quite general and can in principle accommodate the variety of situations mentioned above, and many more: basic domain adaption, multi-domain adaptation with various target distributions, possibly including domains unseen in training. In our experiments, we would like to better assess the true potential of MDAC is these settings and seek to experimentally answer the following questions:
\begin{itemize}
\item is MDAC a viable alternative to conventional finetuning? In particular, does it enable to better take advantage of relevant data from other domains?
\item is MDAC also a viable option in multi-domain adaptation scenarios?
\item does MDAC also enable to perform \emph{unsupervised} (multi-)domain adaptation? \fyDone{TBContinued}
\end{itemize}
These questions are further explored in section~\ref{sec:results}. We now turn to our experimental conditions.

@@

We randomly select in each corpus a development and a test set of 1,000 lines and keep the rest for training. Validation sets are used to chose the best model according to the average BLEU score \cite{Papineni02bleu}.\footnote{We use truecasing and the \texttt{multibleu} script.}\fyDone{A word about meta-parameter settings} Significance testing is performed using bootstrap resampling \cite{Koehn04statistical}, implemented in compare-mt\footnote{\url{https://github.com/neulab/compare-mt}} \cite{Neubig19compare-mt}. We report significant differences at the level of $p=0.05$.\fyDone{Fix correct p value}

@@

\begin{itemize}
\itemsep0em 
\item Generic models trained with various predefined mixtures of the training data taking the form:
\begin{align} \label{mixture:trn}
\lambda_{\alpha}(d) = \frac{q_d^{\alpha}}{\displaystyle{\mathop{\sum}_{d=1}^{n_d}q_d^{\alpha}}} &&
q_d = \frac{\mid N^{s}_d \mid}{\displaystyle{N^{s}}} % \mathop{\sum}_{i=1}^K\mid D_i \mid}}
\end{align} \setlength{\abovedisplayskip}{2pt}
\setlength{\belowdisplayskip}{2pt} 
with $\alpha \in [0,0.25,0.5,0.75,1.0]$. These systems are denoted \system{Mixed-$\alpha$} below. \system{Mixed-$0$} uses a uniform domain distribution, \system{Mixed-$1.0$} uses the observed domain distribution.
\item finetuned models \citep{Luong15stanford,Freitag16fast}, based on the \system{Mixed-$1.0$} system, further trained on each domain for at most 50~000 iterations, with early stopping when the dev BLEU stops increasing.\fyTodo{for ?? iterations} The full finetuning (\system{FT-Full}) procedure may update all the parameters of the initial generic model, resulting in six systems each adapted for one domain, with no parameter sharing across domains.

\item Our comparison of multi-domain systems\fyTodo{CL is only dynamic ?} includes baselines with fixed data mixtures corresponding to $\lambda^l \in \big[ \lambda_0, \lambda_{0.25}, \lambda_{0.5}, \lambda_{0.75}, \lambda_{1.0}\big]$, and our reimplementations of recent proposals from the literature: Curriculum Learning (CL) of \citet{Zhang19curriculum} and Differential Data Selection (DDS) of \citet{Wang20balancing}.
\end{itemize}

@@

In our work, we simply parameterize the distribution $\lambda^l$ as follows (with $\beta=2$ in all our experiments):\fyTodo{Explain why}
\begin{equation}
\lambda
^l(d;\vpsi) = \frac{\vpsi[d]^\beta}{\sum_i \vpsi[i]^\beta}. \nonumber
\end{equation}

Additional choices for the hyper-parameters of our method include the number of simulation steps $k=10$ and the learning rate $\mathbf{lr}_{data}=0.001$. We update the sampling distribution via 100 gradient descent iterations for almost all experimental settings except that for adaptation with automatic clusters (Section \ref{ssec:clda}), where we use 20 gradient descent iterations.\fyTodo{Why? computation?} We split the training into 100 short sessions that last 2000 training steps each. The choice of those hyper-parameters is mostly heuristic except for the learning rate $\mathbf{lr}_{data}$ which is optimized via grid search over a range of values $[0.001,0.0025,0.005]$.

@@

In the domain adaptation task, given the data from 6 domains (\domain{med}, \domain{bank}, \domain{law}, \domain{it}, \domain{talk}, \domain{rel}), we aim to build distinct expert NMT models for each domain.

@@

In the bi-domain adaptation task, given again same 6 domains, we only focus on adapating only to 2 domains.

In the fourth experiment, given training data in 6 domains and a small development set of an new domain, (\domain{News} in our case) we aim to build an NMT model which will perform well on test data from the unseen domain.

@@

\subsection{Domain Adaptation}\label{ssec:da}
In this setting, we aim to build an expert NMT model in only one domain. This setting corresponds to Dirac distribution $\lambda^t$, in which the probability of domains is 0 except for one domain.

We initialize MDAC and DDS by 3 different distributions $\lambda_0$, $\lambda_1$ and $\lambda_d$. According to Table \ref{tab:da}, MDAC achieves the best performance with $\lambda_0$ initial where all domains have the same probability to be chosen, though $\lambda_0$  initialization only improve significantly $\lambda_d$ initialization in small domains including \domain{talk},\domain{bank}and\domain{it}. $\lambda_d$ initialization is beneficial for adapting the NMT system to large domains such as \domain{med} and \domain{law}. The same conclusion is also true for DDS.

We now compare the best MDAC (initialized by $\lambda_0$) to fine-tuning. According to Table \ref{tab:da}, MDAC is outperformed by fine-tuning method in large domains including \domain{med} and \domain{law}. However, MDAC improves fine-tuning by approximately 0.5 BLEU in \domain{bank} and 1.0 BLEU in \domain{rel}. This indicates that for small domains, out-of-domain data can improve the generalization of the NMT model and MDAC is capable to exploit this advantage by balancing the in-domain and the out-of-domain training data instead of edging out the out-of-domain training data as in fine-tuning.

DDS also demonstrates promising results in this task but is always outperformed by MDAC overall. The same conclusion is also applied to the CL method.

\begin{table*}[htbp]
  \centering \small
  \begin{tabular}{|l|*8{r|}} \hline
    domain \hfill $d=$ & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{mean} \\ \hline
    FT-Full($d$) \hfill [BLEU] &37.7&59.2&54.5&34&46.8&90.8&53.8\\ \hline
    \hline
    \system{CL($d$)} &37.2&55.4&53.0&31.3&45.3&90.8&52.2\\ \hline
    \system{DDS($\vlambda_0, \vlambda_d$)} &36.7&56.2&54.3&33.5&46.8&91.8&53.2\\
    \system{MDAC($\vlambda_0, \vlambda_d$)} &36.7&58.2$^{**}$&55$^{*}$&33.3&46.6&91.9$^{***}$&53.6\\
     \hline
    \system{DDS($\vlambda_1, \vlambda_d$)} &36.4&56.3& 45.4& 32.6&44.5&43.1&43.1\\
    \system{MDAC($\vlambda_1, \vlambda_d$)} &37.2&55.1&51.8&32.8&44.9&85.4&51.2 \\ \hline
    \system{DDS($\vlambda_d, \vlambda_d$)} &37.0&59.6&53.7&30.2&45.7&91.6&53.0 \\
    \system{MDAC($\vlambda_d, \vlambda_d$)}&37.9&59.6&53.9&30.4&45.8&92.1&53.3 \\
    \hline
  \end{tabular}
  \caption{We report scores of each method with 6 target domains, and compare with full fine-tuning: each column corresponds to a distinct system. ($^{*}$) MDAC is significantly better than CL, fine-tuning and DDS with $p<0.05$. ($^{**}$) MDAC is significantly better than CL and DDS with $p<0.05$. ($^{***}$) MDAC is significantly better than CL, fine-tuning with $p<0.05$}
  \label{tab:da}
\end{table*}

@@

Multi-domain adaptation task requires best averaged performance of the NMT model in 6 domains. This setting corresponds to the uniform test distribution $\lambda^t = \lambda_0$. In this situation, the method CL of \citet{Zhang19curriculum} can not be applied. We therefore only compare the performance of MDAC, DDS and several fixed training data distribution $\lambda^l \in \big[ \lambda_0, \lambda_{0.25}, \lambda_{0.5}, \lambda_{0.75}, \lambda_{1.0}\big]$. The definition of those notations can be found in the equation \ref{mixture:trn}.

@@

\begin{table*}[htbp]
  \centering \small
  \begin{tabular}{|l|*9{r|}} \hline
    domain \hfill $d=$ & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{mean} & \multicolumn{1}{|c|}{\domain{news}} \\ \hline \hline
    \system{MDAC($\vlambda_1, \vlambda_2$)}&36.2&-&-&-&46.1$^*$&-&-&- \\
    \system{DDS($\vlambda_1, \vlambda_2$)}&36.5&-&-&-&44.4&-&-&- \\
    \system{MDAC($\vlambda_1, \vlambda_2$)}&-&57.2$^*$&53.8$^*$&-&-&-&-&- \\
    \system{DDS($\vlambda_1, \vlambda_2$)}&-&56.1&52.6&-&-&-&-&- \\
    \system{MDAC($\vlambda_1, \vlambda_2$)}&-&-&-&32&-&90&-&- \\
    \system{DDS($\vlambda_1, \vlambda_2$)}&-&-&-&32.9&-&91.1&-&- \\ \hline
  \end{tabular}
  \caption{Non empty columns correspond to the target domains. For a given line, all the non empty columns \emph{correspond to the same bi-domain system}. ($^*$) MDAC is significantly better than DDS with $p<0.05$.}
  \label{tab:bi-da}
\end{table*}
According to Table \ref{tab:bi-da}, MDAC outperforms DDS in 2 over 3 settings including adapting to \domain{med-it} and \domain{law-bank} while being surpassed in \domain{talk-rel}, showing that MDAC is capable to adapt to a variable set of target domains.

>>>>

\section{Introduction}\label{sec:intro}
A typical setting in machine translation (MT) is to collect the largest possible collection of parallel data for the chosen language pair, with the intent to achieve optimal performance for a task of interest. In such situations, the training data distribution is opportunistic, while the test data distribution is chosen and fixed; a key component in training is then to mitigate the detrimental effects of a possible mismatch between these distributions. Single-source and multi-source\footnote{In this context, multi-source refers to simultaneously having multiple domains to adapt from and should not be confused with multi-source translation, where several \emph{source languages} are considered.} domain adaptation (DA) is a well-studied instance of this setting (see \citet{Chu2017comparison} for a review), and so is multi-domain (MD) learning \citep{Chu18multilingual,Zeng18multidomain,Jiang19multidomain,Pham21revisiting}. A related situation is multilingual machine translation \citep{Firat16multiway,Ha16towards,Johnson17google,Arivazhagan19massively}\fyTodo{Fix ref}\revision{cite also \citep{Shen21source}}, where the heterogeneity of training data not only corresponds to variations in topic, genre or register, but also in language.

@@

To compute the reward $R(d)$ of using data from domain $d$ to train the model, we simulate $k$ training steps from current checkpoint by training the model with $k$ batches sampled from $D^l(d)$ and compute the gain of the weighted dev-loss. This computation is inspired by the target prediction gain in \citep{Graves17automated}. However, \citep{Graves17automated} used accumulated gains from the past as reward, while we predict the usefulness of each domain for improving the future performance of the system given its current state. This is achieved by simulating a round of training with only the data from one domain. Furthermore, the choice of the parameterization of the sampling distribution in our method differs from that of \citet{Graves17automated}, although this choice is empirical.

The work of \citet{Wang20balancing} is also related: it is based on the Bi-level Optimization framework, which aims to find an optimal static distribution $\lambda^{l}$ that will result in the best NMT model with respect to a given target dev set at the end of training. These authors also derive a similar form of update for $\psi$. However, their reward is the cosine similarity between the gradient computed with the training data from one domain and the gradient computed with the dev set. We compare this approach with ours in the experiment section.

\subsection{MDAC for (multi) domain adaptation}
The setting developed in previous sections is quite general and can in principle accommodate the variety of situations mentioned above, and many more: basic domain adaption, multi-domain adaptation with various target distributions, possibly including domains unseen in training. In our experiments, we would like to better assess the true potential of MDAC is these settings and seek to experimentally answer the following questions:
\begin{itemize}
\item is MDAC a viable alternative to conventional finetuning? In particular, does it enable to better take advantage of relevant data from other domains?
\item is MDAC also a viable option in multi-domain adaptation scenarios?
\item does MDAC also enable to perform \emph{unsupervised} (multi-)domain adaptation? \fyDone{TBContinued}
\end{itemize}
These questions are further explored in Section~\ref{sec:results}. We now turn to our experimental conditions.

@@

We randomly select in each corpus a development and a test set of 1,000 lines and keep the rest for training. Validation sets are used to chose the best model according to the average BLEU score \citep{Papineni02bleu}.\footnote{We use truecasing and the \texttt{multibleu} script.}\fyDone{A word about meta-parameter settings} Significance testing is performed using bootstrap resampling \cite{Koehn04statistical}, implemented in compare-mt\footnote{\url{https://github.com/neulab/compare-mt}} \citep{Neubig19compare-mt}. We report significant differences at the level of $p=0.05$.\fyDone{Fix correct p value.}\fyTodo{Pourquoi pas sacre BLEU?}

@@

\begin{itemize}
\itemsep0em 
\item Generic models trained with various predefined mixtures of the training data taking the form:
\begin{align} \label{mixture:trn}
\lambda_{\alpha}(d) = \frac{q_d^{\alpha}}{\displaystyle{\mathop{\sum}_{d=1}^{n_d}q_d^{\alpha}}} &&
q_d = \frac{\mid N^{s}_d \mid}{\displaystyle{N^{s}}} % \mathop{\sum}_{i=1}^K\mid D_i \mid}}
\end{align} \setlength{\abovedisplayskip}{2pt}
\setlength{\belowdisplayskip}{2pt} 
with $\alpha \in [0,0.25,0.5,0.75,1.0]$. These systems are denoted \system{Mixed-$\alpha$} below. \system{Mixed-$0$} uses a uniform domain distribution, \system{Mixed-$1.0$} uses the observed domain distribution.
\item finetuned models \citep{Luong15stanford,Freitag16fast}, based on the \system{Mixed-$1.0$} system, further trained on each domain for at most 50~000 iterations, with early stopping when the dev BLEU stops increasing for 5 successive iterations.\fyDone{for ?? iterations} The full finetuning (\system{FT-Full}) procedure may update all the parameters of the initial generic model, resulting in six systems, each adapted for one domain, with no parameter sharing across domains.

\item Our comparison of multi-domain systems\fyTodo{CL is only dynamic ?} includes baselines with fixed data mixtures corresponding to $\vlambda^l \in \big[ \vlambda_0, \vlambda_{0.25}, \vlambda_{0.5}, \vlambda_{0.75}, \vlambda_{1.0}\big]$, and our reimplementations of recent proposals from the literature: Curriculum Learning (CL) of \citet{Zhang19curriculum} and Differential Data Selection (DDS) of \citet{Wang20balancing}.
\end{itemize}

@@

In our work, we simply parameterize the distribution $\vlambda^l$ as follows (with $\beta=2$ in all our experiments):\fyTodo{Explain why}
\begin{equation}
\lambda
^l(d;\vpsi) = \frac{\vpsi[d]^\beta}{\sum_i \vpsi[i]^\beta}. \nonumber
\end{equation}

Additional choices for the hyper-parameters of our method include the number of simulation steps $k=10$ and the learning rate $\mathbf{lr}_{data}=0.001$. We update the sampling distribution via 100 gradient descent iterations for almost all experimental settings except that for adaptation with automatic clusters (Section~\ref{ssec:clda}), where we use only 20 gradient descent iterations.\footnote{This is intended to regularize the training of $\psi$ and avoid converging towards degenerate solutions where some clusters get no training samples.}\fyDone{Why? computation?} We split the training into 100 short sessions that last 2000 training steps each. The choice of those hyper-parameters is mostly heuristic except for the learning rate $\mathbf{lr}_{data}$ which is optimized via grid search over a range of values $[0.001,0.0025,0.005]$.

@@

In the domain adaptation task, given the data from 6 domains (\domain{med}, \domain{bank}, \domain{law}, \domain{it}, \domain{talk}, \domain{rel}), we aim to build distinct expert NMT models for each domain. In the bi-domain adaptation task, given again same 6 domains, we only focus on adapting only to 2 (known) domains.

@@

In the fourth experiment (few shot adaptation)\fyTodo{or weakly supervised ?}, given training data in 6 domains and a small development set of a new domain, (\domain{News} in our case), our goal is to build an NMT model which will perform well on test data from the unseen domain.

@@

\subsection{Domain Adaptation}\label{ssec:da}
In this setting, we aim to build an expert NMT model in only one domain. This setting corresponds to Dirac distribution $\vlambda^t$, in which the probability of domains is 0 except for one domain.

We initialize MDAC and DDS by 3 different distributions $\vlambda_0$, $\vlambda_1$ and $\vlambda_d$. According to Table~\ref{tab:da}, MDAC achieves the best performance with $\vlambda_0$ (uniform domain distribution) as the initial value, though $\vlambda_0$  initialization only significantly improves over $\vlambda_d$ initialization in small domains such as \domain{talk},\domain{bank} and\domain{it}. Initializing with $\vlambda_d$ seems more appropriate when targeting large domains such as \domain{med} and \domain{law}. The same conclusions also hold for DDS.

We now compare the best MDAC system (initialized with $\vlambda_{t=0} = \vlambda_0$) to full finetuning. According to Table~\ref{tab:da}, MDAC is outperformed by fine-tuning method in large domains including \domain{med} and \domain{law}. However, MDAC improves fine-tuning by approximately 0.5 BLEU in \domain{bank} and 1.0 BLEU in \domain{rel}. This indicates that for small domains, out-of-domain data can improve the generalization of the NMT model and MDAC is capable to exploit this advantage by balancing the in-domain and the out-of-domain training data instead of edging out the out-of-domain training data as in fine-tuning.

DDS also demonstrates promising results in this task, but is always outperformed by MDAC overall. The same conclusions also hold for the CL method.\fyTodo{Continue}

\begin{table*}[htbp]
  \centering \small
  \begin{tabular}{|l|*8{r|}} \hline
    domain \hfill $d=$ & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{mean} \\ \hline
    FT-Full($d$) &37.7&59.2&54.5&34&46.8&90.8&53.8\\ \hline
    \hline
    \system{CL($d$)} &37.2&55.4&53.0&31.3&45.3&90.8&52.2\\ \hline
    \system{DDS($\vlambda_0, \vlambda_d$)} &36.7&56.2&54.3&33.5&46.8&91.8&53.2\\
    \system{MDAC($\vlambda_0, \vlambda_d$)} &36.7&58.2$^{**}$&55$^{*}$&33.3&46.6&91.9$^{***}$&53.6\\
     \hline
    \system{DDS($\vlambda_1, \vlambda_d$)} &36.4&56.3& 45.4& 32.6&44.5&43.1&43.1\\
    \system{MDAC($\vlambda_1, \vlambda_d$)} &37.2&55.1&51.8&32.8&44.9&85.4&51.2 \\ \hline
    \system{DDS($\vlambda_d, \vlambda_d$)} &37.0&59.6&53.7&30.2&45.7&91.6&53.0 \\
    \system{MDAC($\vlambda_d, \vlambda_d$)}&37.9&59.6&53.9&30.4&45.8&92.1&53.3 \\
    \hline
  \end{tabular}
  \caption{We report BLEU scores of each method with 6 target domains, and compare with full fine-tuning: each column corresponds to a distinct system. ($^{*}$) MDAC is significantly better than CL, fine-tuning and DDS with $p<0.05$. ($^{**}$) MDAC is significantly better than CL and DDS with $p<0.05$. ($^{***}$) MDAC is significantly better than CL, fine-tuning with $p<0.05$}
  \label{tab:da}
\end{table*}

@@

Multi-domain adaptation task requires best averaged performance of the NMT model in 6 domains. This setting corresponds to a uniform test distribution $\vlambda^t = \vlambda_0$. In this situation, the CL method of \citet{Zhang19curriculum} does not apply. We therefore only compare the performance of MDAC, DDS and several fixed training data distribution $\lambda^l \in \big[ \lambda_0, \lambda_{0.25}, \lambda_{0.5}, \lambda_{0.75}, \lambda_{1.0}\big]$ (see equation~\eqref{mixture:trn}).

@@

\begin{table*}[htbp]
  \centering \small
  \begin{tabular}{|l|*7{r|}} \hline
    domain \hfill $d=$ & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} \\ \hline \hline%  \multicolumn{1}{c|}{mean} & \multicolumn{1}{|c|}{\domain{news}} 
    \system{MDAC($\vlambda_0, \vlambda_2$)}&36.2&-&-&-&46.1$^*$&-&\\
    \system{DDS($\vlambda_0, \vlambda_2$)}&36.5&-&-&-&44.4&- \\
    \system{MDAC($\vlambda_0, \vlambda_2$)}&-&57.2$^*$&53.8$^*$&-&-&-& \\
    \system{DDS($\vlambda_0, \vlambda_2$)}&-&56.1&52.6&-&-&-&- \\
    \system{MDAC($\vlambda_0, \vlambda_2$)}&-&-&-&32&-&90 \\
    \system{DDS($\vlambda_0, \vlambda_2$)}&-&-&-&32.9&-&91.1 \\ \hline
  \end{tabular}
  \caption{Non empty columns correspond to the target domains. For a given line, all the non empty columns \emph{correspond to the same bi-domain system}. ($^*$) MDAC is significantly better than DDS with $p<0.05$.}
  \label{tab:bi-da}
\end{table*}
According to Table \ref{tab:bi-da}, MDAC outperforms DDS in 2 over 3 settings including adapting to \domain{med-it} and \domain{law-bank} while being surpassed in \domain{talk-rel}, showing that MDAC is capable to adapt to a variable set of target domains.
